Scalar_M1

### 2015-05-15 models/Model_Playspace.Rmd
commented out line
currently can't pass external d.f to mutate function. need work around

  scale.matrix <- data %>% 
    select(stars, degree, speaker.p, prior.p) %>%
    mutate(listener.pred = norm.post(stars, degree, get.m(scale, .)))

  return scale.matrx$
 #BP------->

>>>>

  m = d.m
  s = "liked_loved"
  get.m(s, d.m)

  d.m <- data %>% 
    select(stars, degree, speaker.p, prior.p)

  scale.matrix <- data %>% 
    select(stars, degree, speaker.p, prior.p) %>% 
    rowwise() %>%
    mutate(listener.pred = norm.post(stars, degree, get.m(scale, d.m)))

  #return scale.matrx$
 #BP------->
